%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Taha Bashir} \\ \vspace{1pt}
    \small 517-499-8835 $|$ \href{mailto:tbash@umich.edu}{\underline{tbash@umich.edu}} $|$ 
    \href{https://www.linkedin.com/in/taha-bashir-72962610b/}{\underline{linkedin.com/in/taha-bashir}} $|$
    \href{https://github.com/taha1211}{\underline{https://github.com/taha1211}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan}{Ann Arbor, MI}
      {Bachelor of Science, Minor in Entrepreneurship}{Sep. 2015 -- April 2020}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Software Engineer}{November 2022 -- Present}
      {K1x}{Chicago, IL}
      \resumeItemListStart
        \resumeItem{Contributed to full-stack application development using Angular and Azure-hosted .NET within Docker containers. Focused on complex corporate tax solutions for several company products.}
        \resumeItem{Developed federal tax analysis and corporate financial modeling applications using Angular, .NET, and SQL. Enhanced IRS reporting processes.}
        \resumeItem{Served as the subject matter expert in front-end development with Angular. Optimized UI/UX and asset management, ensuring a superior user experience.}
        \resumeItem{Directed the creation of new calculation technologies for diverse user profiles and data analysis. Utilized system design and algorithmic solutions to analyze and integrate thousands of data points and user objects across the application. Contributions achieved significant SaaS deals and a notable increase in the user base.}
        \resumeItem{Spearheaded the development of a micro-frontend, significantly enhancing usability and performance. Made it the most performant and optimized part of our stack in terms of responsiveness, load times, and usability.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Engineering Lead}{May 2022 -- November 2022}
      {Paani Project}{Ann Arbor, MI}
      \resumeItemListStart
        \resumeItem{Led full-stack development team in major overhaul of non-profit Paani Project tech stack. Spearheaded to entirely new codebase using Astro, React, and Contentful CMS.}
        \resumeItem{Configured custom SEO configurations, lighthouse page optimizations, and analytics tracking for new system in order to improve donation conversion and retention by 10x.}
        \resumeItem{Utilized system design to re-engineer and streamline well development and donation tracking - reducing time spent on manual data entry, and increasing customer transparency regarding donor funds to real-time status.}
        \resumeItem{Developed custom automated Azure CI/CD pipeline to track codebase changes, test functionality, and deploy to production successfully. }
      \resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Chief Technical Officer. Cofounder}{January 2019 -- May 2022}
      {Indus}{Ann Arbor, MI}
      \resumeItemListStart
        \resumeItem{Created wholesale marketplace connecting small businesses, suppliers, and delivery drivers with three products.}
        \resumeItem{Pioneered and managed full-stack development in React Native and GCP, focusing on feature development and application management to enhance customer acquisition and retention. Personally trained and led both new developers and interns in approaching the codebase, and contributing meaningful changes and additions.}
        \resumeItem{Led as chief system architect of 10 developers across two teams - ensuring that the shared services, data models, and scalability of both code bases were aligned and optimal for their given use cases. Heavily leveraged system design principles and serverless lambda functions to allow for greater uptime of core functionalities.}
        \resumeItem{Developed new scalable solutions in delivery routing, inventory management, payment processing, NLP, and large data set analysis, resulting in systems that significantly reduced customer costs by millions in labor and time.}
    \resumeItemListEnd

    \resumeSubheading
      {Product/Software Analyst}{October 2021 -- May 2022}
      {ArborMetrix}{Ann Arbor, MI}
      \resumeItemListStart
        \resumeItem{Functioned in a hybrid capacity as an Analyst, Scrum Master, and Developer, leading the development of custom multi-million dollar reporting software tailored to healthcare clients, utilizing Java, XML, and VBA.}
        \resumeItem{Collaborated closely with clients including hospitals, pharmacies, and larger organizations like the APA, focusing on data insights, patient outcome improvements, and developing new analysis processes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, C\#, JavaScript, TypeScript, Python, VBA, XML, XAML, HTML, CSS, SCSS, Ruby, SQL, Java} \\
     \textbf{Frameworks + Front-End}{: React (TypeScript/JavaScript), React Native, Redux + Ducks/Slices, Node js, Next js, Astro, Angular, Angular JS, Angular NgRx, Monorepos, Micro-frontends, Tailwind CSS, Bootstrap, Express} \\
     \textbf{Backend Technologies + Services}{: Ruby on Rails, .NET Core, .NET Framework, Google Cloud Platform, Serverless (Lambda) Functions, NoSQL DBs (MongoDB, Cloud Firestore), Azure Platform Development, SQL DBs, Node js, Docker, Github Actions, YAML DevOps Pipelines, MVC Model} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
